Resource Buying Games

### 2017-01-07 slides.tex
added example, added soundness intuition

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

@@

\begin{document}
\input{tikz/settings}
\maketitle
\section{Introduction}
\begin{frame}
  % \begin{itemize}
  %   \item Context (1 slide)
  %     \begin{itemize}
  %       \item What is modelled?
  %       \item How is it modelled?
  %     \end{itemize}
  %   \item Example (1 slide)
  %     \begin{itemize}
  %       \item Introducing an example which is used to illustrate different
  %         aspects throughout the presentation
  %       \item Interleaved graphs for two players, both want to acquire a
  %         spanning tree
  %     \end{itemize}
  % \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Example: Graph}
  \resizebox{\textwidth}{!}{\input{tikz/graphp2}}
\end{frame}

\subsection{Correctness}
\begin{frame}
  % \begin{itemize}
  %   \item Intuitively present the ideas for the correctness (1/2 slides)
  %   \item (Formal proofs might take too long?)
  % \end{itemize}
\end{frame}

\section{Weighted Matroid Games}
\begin{frame}
  % \begin{itemize}
  %   \item (2 slides)
  %   \item Introduce socially optimal solution
  %   \item Show (or at least motivate) why this is a PNE
  %   \item Mention reduction to show that finding an optimal solution is NP-hard
  % \end{itemize}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{csquotes}
\usepackage{cancel}
\usetheme{metropolis}
\title{Resource Buying Games}
\author[C. Welzel]{Christoph Welzel}

@@

\begin{document}
\input{tikz/settings}
\maketitle
\section{Introduction}
\begin{frame}
\end{frame}

@@

\begin{frame}
  \frametitle{Example: Graph}
  \begin{columns}
    \column{0.5\textwidth}
    Player 1:\\
    \vspace{-0.2cm}
    \begin{center}
      \resizebox{0.6\textwidth}{!}{\input{tikz/graphp1labeled}}
    \end{center}
    \column{0.5\textwidth}
    Player 2:\\
    \vspace{-0.5cm}
    \begin{center}
      \resizebox{0.6\textwidth}{!}{\input{tikz/graphp2labeled}}
    \end{center}
  \end{columns}
  \begin{center}
    \resizebox{0.35\textwidth}{!}{\input{tikz/graphboth}}
  \end{center}
\end{frame}

\newlength{\cutscaling}
\setlength{\cutscaling}{0.17\textwidth}
\begin{frame}
  \frametitle{Example: Algorithm}
  \begin{columns}
    % left column:
    \column{0.3\textwidth}
    \resizebox{\textwidth}{!}{\alt<1-6>{\input{tikz/graphp1}}{\alt<7>{\input{tikz/graphp1Cont}}{\input{tikz/graphp1ContDel}}}}
    \begin{columns}
      \column{0.5\textwidth}
      \resizebox{\cutscaling}{!}{\alt<1-2>{\input{tikz/graphp1Cut1}}{\input{tikz/graphp1Cut1value}}}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut2}}{\input{tikz/graphp1Cut2value}}}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut3}}{\input{tikz/graphp1Cut3value}}}
      \column{0.5\textwidth}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut4}}{\input{tikz/graphp1Cut4value}}}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp1Cut5}}{\input{tikz/graphp1Cut5value}}}
    \end{columns}

    % middle column:
    \column{0.4\textwidth}
    \resizebox{\textwidth}{!}{\alt<1-8>{\input{tikz/graphbothCosts}}{\input{tikz/graphbothCostsUpd}}}
    \begin{center}
      \uncover<5->{\alt<5>{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3}}}{\resizebox{0.7\textwidth}{!}{\input{tikz/graphp1Cut3marked}}}}
    \end{center}

    % right column:
    \column{0.3\textwidth}
    \resizebox{\textwidth}{!}{\alt<1-7>{\input{tikz/graphp2}}{\input{tikz/graphp2Del}}}
    \begin{columns}
      \column{0.5\textwidth}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut1}}{\input{tikz/graphp2Cut1value}}}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut2}}{\input{tikz/graphp2Cut2value}}}
      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut3}}{\input{tikz/graphp2Cut3deleted}}}
      \column{0.5\textwidth}
      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut4}}{\input{tikz/graphp2Cut4deleted}}}
      \resizebox{\cutscaling}{!}{\alt<1>{\input{tikz/graphp2Cut5}}{\input{tikz/graphp2Cut5deleted}}}
      \resizebox{\cutscaling}{!}{\alt<1-3>{\input{tikz/graphp2Cut6}}{\input{tikz/graphp2Cut6value}}}
    \end{columns}
  \end{columns}
  \uncover<9>{ }
\end{frame}

\begin{frame}
  \frametitle{Soundness}
  \begin{itemize}
    \item Termination:
      \begin{itemize}
        \item inductively applying contraction operations lead to basis
        \item deletion cannot \enquote{loose} bases for other players since
          chosen cut is inclusion-wise minimal
      \end{itemize}
    \item Correctness
      \begin{itemize}
        \item Lemma: cost of the chosen element decreases monotonically in each
          iteration
        \item assume there is a beneficial alternative basis
          $\hat{B} = (B_{i}\setminus\set{g})\cup{f}$
          \begin{itemize}
            \item consider iteration $k$ in which $g$ is added to basis of $i$:
            \item if $f$ is in the corresonponding cut its cost never changes
              since it is deleted from every matroid $rightarrow$ $f$ is not in
              the cut
            \item but $f$ and $g$ \enquote{open} same dimensionality, thus $f$
              is not left in contracted matroid of $i$
            \item $f$ was deleted before (in this iteration the cost of the
              chosen element was lower than for $f$ in contradiction to lemma)
          \end{itemize}
      \end{itemize}
  \end{itemize}
\end{frame}

\section{Weighted Matroid Games}
\begin{frame}
  % \begin{itemize}
  %   \item (2 slides)
  %   \item Introduce socially optimal solution
  %   \item Show (or at least motivate) why this is a PNE
  %   \item Mention reduction to show that finding an optimal solution is
  %     NP-hard
  % \end{itemize}
\end{frame}

### 2017-01-07 tikz/graphp1ContDel.tex
added example, added soundness intuition

\begin{tikzpicture}
  \node[node] (A) {};
  \node[below=0.5 of A] (d1) {};
  \node[node, below=0.5 of d1] (B) {};
  \node[right=1 of A] (d2) {};
  \node[node, right=1 of d2] (D) {};
  \node[node] (C) at (d1-|d2) {};
  \node[node] (E) at (B-|D) {};
  \node[node, above=0.5 of d2] (F) {};

  \draw[edge, p1] (A) to node[right, black, label={[black,label distance=-0.2cm]right:\tiny$8$}] {\tiny\bcancel{$7$}} (B);
  \draw[edge, both, dotted] (A) to node[above, black] {\tiny$8$} (C);
  \draw[edge, p1] (B) to node[below, black] {\tiny$2$} (C);
  \draw[edge, both] (C) to node[above, black] {\tiny$3$} (D);
  \draw[edge, p1] (C) to node[below, black] {\tiny$6$} (E);
  \draw[edge, p2] (A) to node[above, black] {\tiny$5$} (F);
  \draw[edge, p2] (D) to node[above, black] {\tiny$2$} (F);
\end{tikzpicture}

>>>>

\begin{tikzpicture}
  \node[node] (A) {};
  \node[below=0.5 of A] (d1) {};
  \node[node, below=0.5 of d1] (B) {};
  \node[right=1 of A] (d2) {};
  \node[node, right=1 of d2] (D) {};
  \node[node] (C) at (d1-|d2) {};
  \node[node] (E) at (B-|D) {};

  \node[fit=(A) (B), draw, rectangle, rounded corners, black] (new) {};

  \draw[edge, p1, bend right, dotted] (C) to (new.east);
  \draw[edge, p1, bend left] (C) to (new.east);
  \draw[edge, p1] (A) to (B);
  \draw[edge, p1] (C) to (D);
  \draw[edge, p1] (C) to (E);
\end{tikzpicture}
